A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-09-09 paper/main.tex
paper: replace kruisproduct

\begin{wrapfigure}{r}{0.25\textwidth}
\begin{center}
\includegraphics[width=40mm]{../graphs/kruisproduct.pdf}
\end{center}
\caption{squarefreeness of an embeddable graph
\label{fig:crossproduct}}
\end{wrapfigure}

@@

            ;
        \end{tikzpicture}
        \qquad
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
            \draw
                (45:0.5) node[p]{} -- (135:0.5) node{}
                                -- (225:0.5) node{}
                                -- (315:0.5) node{}
                (15:1.3) node[p]{}
                (345:1.3) node[p]{}
                (195:1.3) node[p]{}
                (165:1.3) node[p]{}

>>>>

\begin{wrapfigure}{r}{0.25\textwidth}
\begin{center}
\begin{tikzpicture}[scale=1.9,thick,
    partial ellipse/.style args={#1:#2:#3}{
            insert path={+ (#1:#3) arc (#1:#2:#3)}
        }]
    \draw (0,0) [partial ellipse=360:180:1 and 0.3] ;
    \draw[gray,dashed] (0,0) [partial ellipse=0:180:1 and 0.3] ;
    \draw (0,0) [rotate=315,partial ellipse=360:180:1 and 0.3] ;
    \draw[gray,dashed] (0,0) [rotate=315,partial ellipse=0:180:1 and 0.3] ;
    \draw (0,0) circle (1) ;
    \node[circle,inner sep=1pt,fill] at (90:1) {};
    \node[above] at (90:1) {$v$};
    \node[circle,inner sep=1pt,fill] at (45:1) {};
    \node[right] at (45:1) {$w$};
\end{tikzpicture}
\end{center}
\caption{squarefreeness of an embeddable graph
\label{fig:crossproduct}}
\end{wrapfigure}

@@

            ;
        \end{tikzpicture}
        \qquad
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
            \draw
                (45:0.5) node[p]{} -- (135:0.5) node[p]{}
                                -- (225:0.5) node[p]{}
                                -- (315:0.5) node[p]{}
                (15:1.3) node[p]{}
                (345:1.3) node[p]{}
                (195:1.3) node[p]{}
                (165:1.3) node[p]{}
